---
title: "Learning R (intermediate DDEA R course)"
author: "Emma"
format: html
---

## R setup
FS package is good to find files in your project
```{r setup}
library(tidyverse)
library(here)
library(snakecase)
library(fs)
source(here("R/functions.R"))
```

## Importing new data (15)
to_snake_case makes it more reable, so none of the coloums are in uppercase. 
n_max determines how many row are loaded from this file
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```

## Exercise: Reading another file (15)

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```

```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```

##Bundling code into functions (16)

```{r}
#' Add two number together
#'
#' @param num1 A number here
#' @param num2 A number here
#'
#' @returns Returns the sum of two numbers
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read()
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()
```

## Exercise (16)

```{r}
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

##Using Map
recurse means that it looks in all the folders, and if there is a folder in a folder it also looks in that one
```{r}
hr_files <- here("data-raw/nurses-stress/stress/") %>%
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)

hr_files

hr_data <- hr_files %>%
  map(read)

hr_data <- hr_files %>%
  map(read) %>%
  list_rbind(names_to = "file_path_id")

hr_data
```

#### Exercise: Convert map to function and use on sleep. (18)
```{r}
#' Read all `.csv.gz` files in the `stress/` folder into one data frame.
#'
#' @param filename The name of files in the sub-folders that we
#'    want to read in.
#'
#' @returns A single data frame/tibble.
#'
read_all <- function(filename) {
  files <- here::here("data-raw/nurses-stress/") |>
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files |>
    purrr::map(read) |>
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}

read_all("HR.csv.gz")
read_all("IBI.csv.gz")
```

##Processing strings with regular expressions (19)
```{r}
hr_data <- read_all("HR.csv.gz")

survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()

hr_data
survey_data
```

##Extract the ID
```{r}
hr_data %>%
  mutate(
    id = str_extract(file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) %>%
      str_remove("/stress/") %>%
      str_remove("/"),
    .before = file_path_id
  ) %>%
  select(-file_path_id)
```

##Exercise: Convert ‘get ID’ code into a function (19)

```{r}
get_participant_id <- function(data) {
  data_with_id <- data |>
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        "/stress/[:alnum:]{2}/"
      ) |>
        stringr::str_remove("/stress/") |>
        stringr::str_remove("/"),
      .before = file_path_id
    ) |>
    dplyr::select(-file_path_id)
  return(data_with_id)
}
```
